\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-10 ms.tex
comments

We measure the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
The control fields are designed to, together, have the same total area as the cluster field. \yumi{Any changes if you pick different control fields?}
The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.

>>>>

We measure the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.
